\documentclass{article}

\usepackage[margin=.75in,tmargin=.3in,bmargin=.3in]{geometry} % For margins
\usepackage{hyperref} % For hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,
	urlcolor=blue,
	citecolor=black,
}
\usepackage{color, soul} % For highlighting
\usepackage{titlesec}
\usepackage{enumitem} % For removing list indent
\usepackage[absolute,overlay]{textpos}
\usepackage{setspace}

\setlength{\parindent}{0pt}

\TPGrid[1in,1in]{2}{9}

\begin{document}

\begin{textblock}{1}(1, 0)
\textbf{\Huge Richard McCoy}

\href{willway@outlook.com}{willway@outlook.com},
\href{richardmccoy@ufl.edu}{richardmccoy@ufl.edu}

\Large

\textbf{Major}: \textit{Electrical Engineering}

\textbf{Professional Hightlights}:
Linux, \\
C/C++,
Embedded Systems,
FPGA,
Signal Processing,
Electromagnetics,\\
Research,
Web Development
\end{textblock}

\begin{textblock}{2}(0, 2)

\setstretch{1.25}
\large


Richard ``Will'' McCoy is a senior Electrical Engineering student at the University of Florida, though he has also taken a majority of the courses required for a Computer Science degree.
He is passionate about the digital side of Electrical Engineering and has experience with embedded systems, operating systems, and FPGA technology.
Will has additionally studied signal processing and electromagnetism due to his interest in radio communications.
He is also a member of the UF chapter of Eta Kappa Nu (HKN), the Honors Society of IEEE. \\

Will has had several opportunities to apply his studies.
In his most recent internship, he worked at VerdeGo Aero, where he was responsible for evaluating various controller architectures (microcontroller vs FPGA) for the FADEC in a 180kW airplane hybrid power plant.
Before this, he worked at CACI, where he was responsible for efficiently implementing an adaptive noise cancellation algorithm (Wiener filter) in C++.
Additionally, he currently in his third year of research at Garrett Lab (a plant pathology group), where he creates simulations and tools for modeling the spread of plant diseases.
Prior to this, he worked in a team of undergraduates to publish a paper on techniques to minimize the number of disease tests, titled ``Optimization of Multi Two-Level Batch Testing''.
Finally, he participated with a team in the 2022 Florida Hacks Hackathon, where his team won $2^{nd}$ place for a project to reduce wasteful energy usage.
Will always likes an engineering challenge, and is looking for a job which combines software and hardware to solve difficult problems. \\

In his free time, Will enjoys maintaining his personal website (\href{https://willmccoy.xyz}{https://willmccoy.xyz}), programming, engineering hobby projects, and going to the beach.
He is an avid Linux user, and is currently working on building a kiln and achieving his Amateur Radio Technician's License.

\end{textblock}

\end{document}
