\documentclass{article}

\usepackage[margin=.75in,tmargin=.3in,bmargin=.3in]{geometry} % For margins
\usepackage{hyperref} % For hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,
	urlcolor=blue,
	citecolor=black,
}
\usepackage{color, soul} % For highlighting
\usepackage{titlesec}
\usepackage{enumitem} % For removing list indent
\usepackage{setspace}

\setlength{\parskip}{0em}

\titleformat{\section}
{\bfseries\Large\centering}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\large}
{}
{0em}
{}


\titleformat{\subsubsection}[runin]
{\bfseries\normalsize}
{}
{0em}
{}[:\hspace{10em}]

\titlespacing{\section} {0em} {0em} {.3em}
\titlespacing{\subsection} {0em} {0em} {0em}
\titlespacing{\subsubsection} {0em} {0em} {.25em}

%https://tex.stackexchange.com/questions/55472/how-to-make-text-aligned-left-center-right-in-the-same-line
%\newcommand\textbox[1]{%
  %\parbox{.333\textwidth}{#1}%
%}

\newcommand\midtextbox[1]{%
  \parbox{.6\textwidth}{#1}%
}

\newcommand\outtextbox[1]{%
  \parbox{.2\textwidth}{#1}%
}

\newcommand\halftextbox[1]{%
	%\begin{raggedright}
  \parbox[t]{.475\textwidth}{#1}%
	%\end{raggedright}
}

\newcommand\spacetextbox[1]{%
  \parbox{.05\textwidth}{#1}%
}

\newcommand{\sectionspacing}{\vspace{-0em}} %Edit spacing here to fit to page

%https://tex.stackexchange.com/questions/342790/how-to-remove-the-extra-lines-between-the-items-in-the-enumerate-environment-and

\setlist[itemize]{
  %label={\upshape(\roman*)},
  %leftmargin=0pt‌​,
  %labelwidth=*,
  %align=‌​left,
  nosep
}

%https://tex.stackexchange.com/questions/10684/vertical-space-in-lists
\newenvironment{CustomItemize}
{ \begin{itemize}[leftmargin=1em]
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parindent}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  } 

%https://tex.stackexchange.com/questions/74212/how-can-i-change-the-whitespace-above-and-below-center
\newenvironment{TitleCenter}[1][\topsep]
  {\setlength{\topsep}{#1}\par\kern\topsep\centering}% \begin{mycenter}[<len>]
  {\par\kern\topsep}% \end{mycenter}
\setlength{\parindent}{0pt}% Just for this MWE

% This configure the inter-line spacing, which is a useful parameter to vary
\spacing{.95}

\begin{document}

\thispagestyle{empty}

\begin{TitleCenter}[0em]
\bfseries\huge

%\parskip{0em}
%\parsep{0em}
RICHARD WILLIAM McCOY (WILL)
\end{TitleCenter}
\noindent\outtextbox{\href{willway@outlook.com}{willway@outlook.com}\hfill}\midtextbox{\hfil11 Ponte Vedra Colony Circle, Ponte Vedra Beach, FL 32082-2793\hfil}\outtextbox{\hfill (904) 228-3384} \\
\noindent\outtextbox{\href{https://willmccoy.xyz}{https://willmccoy.xyz}\hfill}\midtextbox{\hfil\hfil}\outtextbox{\hfill}

%\title Richard William McCoy (Will)

%Shift up, because website does not fill full line
\vspace{-1em}
\section{Education}

\noindent
\halftextbox{
\begin{raggedright}
\subsection{University of Florida,  Gainesville, FL}
\begin{CustomItemize}
\item \underline{Overall GPA: 4.0}, Major GPA: 4.0
\item Fall Class of 2025, Senior, 171 credits
\item Student of Bachelor of Science in Electrical Engineering
\item Student of Bachelor of Science in Computer Science
%\item Student of Minor of Mathematics
\end{CustomItemize}

%\vspace{.94em} %Comment/Uncomment for appropriate spacing
\subsection{Relevant Coursework}
\subsubsection{Electrical Engineering}
Circuits 1 and 2,
Digital Logic (FPGA/VHDL),
EE Physics,
Electronic Circuits,
Signals and Systems,
Foundations of DSP,
Electromagnetic Fields 1 and 2,
Microprocessors,
Digital Design,
Reconfigurable Computing,
Communication Systems,
Wireless and Mobile Networks
%\hfill
\end{raggedright}
}
\spacetextbox{\hfil\hfil}
\halftextbox{
%\hfill
\begin{raggedright}
\subsubsection{Mathematics}
Differential Equations,
Calculus III,
Engineering Statistics, 
Linear Algebra,
Discrete Mathematics
\subsubsection{Computer Science}
C++ Programming,
Data Structures,
Software Engineering,
Computer Organization,
Databases,
Operating Systems,
Networking,
Advanced Systems Programming,
Programming Language Concepts

\subsubsection{Other}
Professional Communications for Engineers,
Undergraduate Research,
EE Junior Design,
Integrated Poduct and Process Design

\end{raggedright}
%\subsection{Current Semester's Relevant Coursework}
}

%\hl{
%Stanton College Preparatory School, Class of 2020, Jacksonville, FL
%International Baccalaureate Diploma Programme graduate
%Weighted GPA: 4.94
%35 on ACT; 1530 on SAT (770 Math and 760 Evidence-Based Reading and Writing)
%Relevant Coursework: AP Calculus AB and BC, AP Physics C Mechanics and E\&M, AP/IB Computer Science
%(Java), AP/IB Physics 1\&2, AP Statistics, AP/IB Chemistry
%}

\sectionspacing{}

\section{Work Experience}
\subsection{Aeronix - Electrical Engineering Design Intern (Summer 2024)}
\begin{CustomItemize}
\item Worked on project to create bit error rate tester, which featured ten 1Gbps SFP interfaces and a FMC connector.
\item Took existing schematic (based around Zynq Ultrascale+ ZU7CG, 900-pin BGA) and adapted it for use case.
\item Began work on modifying existing layout to reflect updated schematic.
\item Created HTML/JS webpage and C++ HTTP server to interact with AXI peripherals loaded on FPGA.
\end{CustomItemize}

\subsection{Ionospheric Radio Lab - Undergraduate Researcher (Spring 2024 - Current)}
\begin{CustomItemize}
\item Member of lab which focuses on studying electromagnetic phenomena in the iohosphere.
\item Worked on project to convert ULF/VLF receiver station software from Windows to Linux.
\item Worked on project to compare two implementations of atmospheric chemistry model, with triangular interpolation.
\item Will travel to University of Alaska to participate in PARS 2024, and use the HAARP transmitter.
\end{CustomItemize}

\subsection{VerdeGo Aero - Electrical Engineering Intern (Summer 2023)}
\begin{CustomItemize}
\item Used anemometers and pressure transducers to measure airflow in a blower system.
\item Created LabView VI to collect, display, and log data from ESP32 and NI DAQ.
\item Proposed high-level design of a FADEC, evaluated both microcontroller and FPGA solutions.
\item Performed electrical power calculations for $1.5\:MW$ generator system.
\end{CustomItemize}

%\subsection{Garrett Plant Pathology Lab - Paid Undergraduate Researcher (Fall 2020 - Current)}
%\begin{CustomItemize}
%\item Program and model in R to simulate pathogen spread in Ethiopian seed trade networks.
%%\item Utilize impact network analysis, an application of graph theory.
%%\item Work with team of 3, writing paper to be published in research journal.
%\item Migrate lab codebase into an object-oriented paradigm.
%\item Design Shiny user interface to allow non-coders to run simulations.
%\item Presented research at Florida Undergraduate Research Conference in February 2022.
%\end{CustomItemize}

\subsection{CACI - Signal Processing Intern (Summer 2022)}
\begin{CustomItemize}
\item Created adaptive interference cancellation filter using a gradient descent algorithm.
\item Prototyped and tested filter in Python, then efficiently implemented filter using C++ in XMidas.
\item Using multithreading, achieved approximately 80 MHz bandwidth on desktop hardware.
\item Created XMidas primitive to stream data from RTL-SDR.
\end{CustomItemize}

\subsection{University of Florida - Published Research (Spring 2021)}
\begin{CustomItemize}
\item Led team of three in researching batch testing, a technique used to minimize the number of disease tests.
\item Proposed method which was shown to be more efficient than comparable models under COVID-like conditions.
\item Wrote simulation in Java with C++ JNI components, analyzed output and generated graphics with R.
\item Head authored paper published in UF Journal of Undergraduate Research in October 2021, titled ``Optimization of Multi Two-Level Batch Testing''.
\item Presented research at Florida Undergraduate Research Conference in February 2022.
\end{CustomItemize}

\subsection{Winsight - Programmer (Winter 2020 - Summer 2021)}
\begin{CustomItemize}
\item Programmed for startup company which seeks to integrate live streaming into youth sports.
\item Utilized React for website, React Native for mobile app, and AWS for backend.
\item Created interface for high-level administration of infrastructure and users.
\item Worked remotely using agile methodology.
\end{CustomItemize}

%\subsection{Duos Technology - Engineering Internship (Summer 2020)}
%\begin{CustomItemize}
%\item Shadowed Electrical Engineers working on a product which scanned rail cars for defects.
%\item Performed destructive failure analysis on damaged scanner unit.
%\item Worked with ground truth team to label images of rail cars.
%\item Wrote program on Raspberry Pi which provided a HTTP REST API to control lights in the scanner.
%\end{CustomItemize}

%\subsection{US Navy - Science and Engineering Apprenticeship Program (SEAP) (Summer 2019)}
%\begin{CustomItemize}
%\item Shadowed Mechanical, Electrical, Chemical, and Material Engineers at the Fleet Readiness Center Southeast at Naval Air Station Jacksonville.
%\item Wrote computer program to analyze time lapses of lengthy chemical reactions to determine their completion.
%\item Delivered presentations of findings and experiences to engineers and other interns on a biweekly basis.
%\end{CustomItemize}

%\subsection{Genesee-Wyoming Railroad Company - Internship (Summer 2018)}
%\begin{CustomItemize}
%\item Shadowed several engineers while learning about the workings of their department, railroad track maintenance, and railroad regulations.
%\item Engaged with engineers on civil engineering in the railroad industry and the digital modeling of planned track.
%\end{CustomItemize}

%\section{Activities and Achievements}

%\hl{
%Member of North Florida Council Troop 27 from 2013 to 2019
%Leadership positions include Senior Patrol Leader, Scribe, Troop Guide, Instructor, and Assistant SPL
%}

\sectionspacing{}
\section{Awards and Honors}

\subsubsection{HKN}
Member of UF chapter of Eta Kappa Nu, the honor society of IEEE

\subsubsection{2022 Florida Hacks}
Placed 2\textsuperscript{nd} in national IBM-sponsored hackathon with project to reduce energy usage

%\subsubsection{University of Florida Dean's List}
%Have been on the Engineering College's Dean's List every semester

\subsubsection{2020 National Merit Scholar}
Recipient of the Benacquisto Scholarship to the University of Florida
%National AP Scholar and AP Scholar with Distinction - Score of 5 on sixteen AP Exams

\subsubsection{Eagle Scout}
Boy Scouts of America,
designed and led construction of two softball dugouts for project

\sectionspacing{}
\section{Additional Skills}

\noindent\halftextbox{

\begin{CustomItemize}
%\item Data analysis using Excel and other spreadsheet programs
\item Fluency: Java, C, C++
\item Competency: JavaScript, HTML, CSS, Go, \LaTeX{}, MATLAB, R, SQL, VHDL, Verilog, Julia, LabVIEW
\end{CustomItemize}
\hfill}
\spacetextbox{\hfil\hfil}
\halftextbox{\hfill
\begin{CustomItemize}
\item Linux, git, and Microsoft Office
\item 3D parametric modeling and printing
\item Embedded Systems
\end{CustomItemize}
}
%\section{Community Service}
%\begin{CustomItemize}
%\item Buddy at Camp I Am Special in the summers of 2017, 2018 and 2019 for a total of 363 service hours
%\item Led own Eagle Scout Project to construct two dugouts for Holy Family Catholic School, as well as other various Eagle projects, including installing and painting fences and building benches
%\end{CustomItemize}

\end{document}
