\documentclass{article}

\usepackage[margin=.9in]{geometry} % For margins
\usepackage{hyperref} % For hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,
	urlcolor=blue,
	citecolor=black,
}
\usepackage{color, soul} % For highlighting
\usepackage{titlesec}
\usepackage{enumitem} % For removing list indent
\usepackage{setspace} 
\pagenumbering{gobble}

\setlength{\parskip}{0em}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parsep}{0pt}


\begin{document}
Richard ``Will'' McCoy \\
33010403 Fletcher Hall \\
Gainesville, FL \\
32612-3301 \\
United States \\
(904) 228-3384 \\
\href{richardmccoy@ufl.edu}{richardmccoy@ufl.edu} \\

November 7, 2021 \\

1441 Bledsoe Drive
Gainesville, FL \\
32612-3301 \\
United States \\

\onehalfspacing

Greetings CORE Hiring Team, \\

I am very interested in applying for the position of TRiP Leader.
After hearing about the program and the opportunities it offers from a current member, I was hooked, and was eager to throw my hat in the ring.
At UF, I am an Electrical Engineering and Computer Science double major, with a 4.0 GPA and 85 credits.
I am also an Eagle Scout, with extensive outdoors and leadership experience.
Ultimately, I believe I have valuable skills to offer your program, and I believe it will give me the opportunity to hone my leadership skills and further enjoy the outdoors.
\\

I have useful experience to offer this program.
As I just mentioned, I was very active with the Boy Scouts of America, an organization which develops outdoors and leadership skills.
Part of becoming an Eagle Scout requires the design and completion of a service project, and in my case I led the construction of two dugouts.
This involved substantial individual planning and project management, and leadership of around 30 people to actually construct it.
In addition to this, through Scouts, I was very involved in leadership positions within my Troop.
Though I had several, my most relevant one was Senior Patrol Leader, which is essentially a Troop president.
In this role, I was responsible for planning Troop activities and campouts, and managing the outdoors skill progression of younger Troop members.
I also have had several jobs, in which I have had a range of responsibilities.
These include leading teams, working within self-organizing teams, working independently, and learning from superiors.
With these experience, I would be able to effectively learn the ins and outs of being a TRiP leader, and would then be able to effectively lead and educate on the activities that I run.
\\

With this program, I would get the opportunity to rekindle my relationship with the outdoors.
Since leaving Scouts, I have focused mostly on school, and would like to get back into routine campouts and activities.
I also genuinely enjoy educating others in outdoor skills (in particular, knots), because it is fulfilling to pass the torch, and because these skills are important to propagate.
Finally, I am very interested in the leadership opportunities offered through TRiP, even more so because they involve the outdoors.
Thank you very much for considering me for the position of TRiP leader.
\\


Regards,\\
Will McCoy

\end{document}
